Air cargo load and route planning in pickup and delivery operations

### 2023-06-06 CAIE/paper.tex
Table 1.5

@@

\vspace{2.0mm}
\begin{table}[H]
	\centering
	\caption{Testing scenarios}  \label{tab:scenarios}
	\begin{tabular}{c c c }
		\toprule
		{\bf Scenario} & {$K$} & {$L$} \\		
		\midrule
		1 & 2    & \{$1,2$\}           \\
		2 & 3    & \{$1,2,3$\}         \\
		3 & 4    & \{$1,2,3,4$\}       \\
		4 & 5    & \{$1,2,3,4,5$\}     \\
		5 & 6    & \{$1,2,3,4,5,6$\}   \\
		\bottomrule
	\end{tabular}
\end{table}

@@

As the MIP solver was not capable of solving all scenarios in polynomial time or reached the computer's RAM (16 GiB) too early, we decided to execute a relaxed model with the decision variables set to CONTINUOUS (a Gurobi parameter) to obtain the upper bound for the objective function. This approach is much faster than using binary decision variables.

{\color{red}
Let $X_{ij}^k$\/ and $Y_{iq}^k$\/ be CONTINUOUS variables, where $1 \leq i \leq m$, $1 \leq j \leq n_k$, $1 \leq q \leq m_k$\/ and $0 \leq k \leq K$.
}
The upper bound (UB) is the objective function value of a linear programming relaxation of the problem, demonstrating that no integer viable solution can have an objective value greater (in maximization) than this.

We solved all scenarios and instances with Gurobi in a {\it MIPGap} parameter equal to 1\% to control the minimal quality of the returned solution, without a time limit.

Note that, in Table \ref{tab:20} all $Gurobi\ f$\/ values are italicized to indicate that these values are at most 1\% distant from the optimal solution.

@@

\begin{table}[H]
\centering
\caption{Methods and scenarios with $surplus =1.2$ and the least cost tours criteria}  \label{tab:20leastcost}
\footnotesize
\begin{tabular}{c|c|cccc}
\toprule
$method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4}  \\
\toprule
\multirow{2}{*}{\it Gurobi* } & $f$ & 7.90    & 11.46   & 12.82   & 13.40     \\
&               {\bf run time (s)}  & 10      & 8       & 11      & 11      \\ 
\midrule[.1pt]	
\multirow{2}{*}{\it Shims}    & $f$ & 7.83    & 11.34   & 12.77   & 13.20    \\
&         {\bf run time (s)}        & 4       & 5       &  6      & 7        \\ 
\bottomrule
\multicolumn{6}{c}{*integer relaxed variables}
\end{tabular}
\normalsize
\end{table}

\begin{table}[H]
\centering
\caption{Methods and scenarios with $surplus =1.2$}  \label{tab:20}
\footnotesize
\begin{tabular}{c|c|ccccc|c}
\toprule
$method$& {\bf Scenarios}                 &{\bf 1}&{\bf 2} & {\bf 3}      & {\bf 4}      & {\bf 5}  & \specialcell{{\bf Normalized}\\{\bf Speed-up}}  \\
\midrule[.1pt]
{\it Gurobi}     & UB for $f$           & {\it 8.91} & {\it 12.92} & {\it 15.12} & {\it 16.29} & {\it 15.34} & -  \\ %51,84
\toprule

\midrule[.1pt]	
\multirow{2}{*}{\it Shims}   & $f$      & 8.43       & 12.77       & 14.47       & 16.28       & 15.15          &   \\
&{\bf run time (s)}                     & 4          &  8          &  33         & 93          & 560          &   \\

@@

@@

>>>>

\usepackage{textcomp}
\usepackage{graphicx} 
\setlength{\fboxsep}{0.005pt}
\newcommand{\tmpframe}[1]{\fbox{#1}}

@@

\vspace{2.0mm}
\begin{table}[H]
	\centering
	\caption{Testing scenarios}  \label{tab:scenarios}
	\begin{tabular}{c c c c}
		\toprule
		{\bf Scenario} & {$K$} & {$L$} & {Shortest tours} \\		
		\midrule
		1 & 2    & \{$1,2$\}           & 0 1 2 0 \\
		2 & 3    & \{$1,2,3$\}         & 0 1 2 3 0 \\
		3 & 4    & \{$1,2,3,4$\}       & 0 4 1 2 3 0 \\
		4 & 5    & \{$1,2,3,4,5$\}     & 0 4 1 2 5 3 0 \\
		5 & 6    & \{$1,2,3,4,5,6$\}   & 0 4 1 2 6 5 3 0 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

As the MIP solver was not capable of solving all scenarios in polynomial time or reached the computer's RAM (16 GiB) too early, we decided to set the Gurobi {\it MIPgap} parameter to 1\% to control the minimal quality of the returned solutions and abbreviate the solution time.

More details on the Gurobi {\it MIPgap} refer to \cite{mipgap}.

@@

\begin{table}[H]
\centering
\caption{Solutions with $surplus =1.2$\/ with the direct and reverse least cost tours.}  \label{tab:20}
\footnotesize
\begin{tabular}{c|c|ccccc|c}
\toprule
$method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
\toprule
\multirow{2}{*}{\it Gurobi* } & $f$ & 8.52    & 11.70   & 13.07   & 13.54 & 12.44     &  1.00\\ % 5927
&               {\bf run time (s)}  & 17      & 17       & 16      & 17   & 26        &  1.0 \\ % 93
\midrule[.1pt]	
\multirow{2}{*}{\it Shims}    & $f$ & 7.83    & 11.34   & 12.77   & 13.20 & 12.22     &  0.97 \\ % 5736
&         {\bf run time (s)}        & 4       & 5       &  6      & 7     & 10        &  2.9  \\ % 32

\bottomrule
\multicolumn{8}{c}{Average $f$ and run time values of K! tours.}\\
\toprule

\multirow{2}{*}{\it Gurobi* } & $f$ & 8.51    & 12.25   & 13.32   & 14.61  & x     &  \\ % 5927
&               {\bf run time (s)}  & 25      & 36      & 121     & 297    & x        &  1.0 \\ % 93
\midrule[.1pt]	
\multirow{2}{*}{\it Shims}    & $f$ & 8.11    & 12.18   & 13.25   & 14.57  & 14.33     &  0.97 \\ % 5736
&         {\bf run time (s)}        & 4       & 8       & 33      & 95     & 572       &  2.9  \\ % 32
\bottomrule
\multicolumn{8}{c}{*{\it MIPgap} parameter set to 1\%. The $f$ values are \textpm 1\% distant from the optimal solution}\\

\end{tabular}
\normalsize
\end{table}

97\% of 16GiB was the Read-Only Memory (RAM) state before we aborted the Gurobi execution on solving scenario 5 in Table \ref{tab:20}.

\begin{figure}[H]
	\centering
	\tmpframe{\includegraphics[scale=0.6]{Images/memory.png}}
	\captionof{figure}{RAM usage on solving scenario 5 by Gurobi (Table \ref{tab:20}).}
	\label{fig:memory}
\end{figure}

\begin{table}[H]
	\centering
	\caption{Solutions with $surplus=1.5$\/ with the direct and reverse least cost tours.}  \label{tab:50}
	\footnotesize
	\begin{tabular}{c|c|ccccc|c}
		\toprule
		$method$          & {\bf Scenarios} & {\bf 1} & {\bf 2} & {\bf 3} & {\bf 4} & {\bf 5} & \specialcell{{\bf Normalized}\\{\bf Speed-up}}   \\
		\toprule
		\multirow{2}{*}{\it Gurobi* } & $f$ &     &    &    &   &   &  \\ % 
		&               {\bf run time (s)}  &     &    &    &   &   &   \\ % 
		\midrule[.1pt]	
		\multirow{2}{*}{\it Shims}    & $f$ &     &    &    &   &   &   \\ % 
		&         {\bf run time (s)}        &     &    &    &   &   &    \\ %

		\bottomrule
		\multicolumn{8}{c}{Average $f$ and run time values of K! tours.}\\
		\toprule

		\multirow{2}{*}{\it Gurobi* } & $f$ & 11.81 & 17.01 & 18.25 & 20.59 & 18.36   &  \\ % 
		&               {\bf run time (s)}  & 53    & 61    & 193   & 470   & 2241    &   \\ % 
		\midrule[.1pt]	
		\multirow{2}{*}{\it Shims}    & $f$ & 11.33 & 16.97 & 17.56 & 20.43 & 17.94   &   \\ % 
		&         {\bf run time (s)}        & 4     & 8     & 34    & 96    & 591     &   \\ % 
		\bottomrule
		\multicolumn{8}{c}{*{\it MIPgap} parameter set to 1\%. The $f$ values are \textpm 1\% distant from the optimal solution}\\

	\end{tabular}
	\normalsize
\end{table}

@@

ESTA TABELA DEVERÁ REFEITA DEPOIS QUE AS ANTERIORES ESTIVEREM PRONTAS.

@@

\bibitem{mipgap} What is the MIPGap? \url{https://support.gurobi.com/hc/en-us/articles/8265539575953-What-is-the-MIPGap-}, 2023.
